Embodied Neuromorphic Benchmarks

### 2015-08-08 paper/paper.tex
intro

We believe embodied benchmarks

>>>>

We believe embodied benchmarks should be of particular interest to
neuromorphic research, given that many of the applications of neuromorphic
hardware are in exactly this domain of embedded and interactive control
of robotic or other physical systems.  However, embodiment raises a number
of issues that complicate the development of such benchmarks.  Rather than
simply providing a data file of inputs and desired outputs, the benchmark
must either specify a full physical system for that embodiment, or it must 
provide software for a simulation of that system.  As we discuss below, either
approach is problematic, and addressing this problem is the primary goal of
this paper.

\section{Embodied Benchmarks}

\subsection{Simulation versus Physical Instantiation}

\subsection{Minimal Simulation}

\subsection{Cheap Robotics}
